Notes on Big MRA

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save.tex
updates on section 2

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

On the other hand, from the second moment we can estimate $Q \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $Q\cdot T_2(0) + \sigma^2$, and consequently $B \equiv Q \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$. Taking the ratio, we obtain the equation:
%
\begin{align}
%
    \frac{1}{Q} + \frac{\sigma^2}{A} = \frac{B}{A}.
%
\end{align}

If we knew $\sigma$, we can solve for $Q$:
%
\begin{align}
%
    Q = \frac{A}{B - \sigma^2}.
%
\end{align}

@@

\section{A quadratic equation satisfied by $\sigma$}

It turns out that $\sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
%
\begin{align}
%
    Q = \frac{A}{B - \sigma^2}.
%
\end{align}

Now we move up to third-order moments. From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (Q \cdot \1^\top x)
        \nonumber \\
    &= Q^2 \cdot w + \sigma^2 \cdot (Q \cdot \1^\top x),
%
\end{align}
%
where 
%
\begin{math}
%
    w = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta).
%
\end{math}

From the observed third-order terms themselves, we can estimate:
%
\begin{align}
%
    D \equiv Q\cdot w + (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x).
%
\end{align}

Consequently:
%
\begin{align}
%
    D\cdot Q - Q \cdot (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)
    = Q^2 \cdot w = C - \sigma^2 \cdot (Q \cdot \1^\top x),
%
\end{align}
%
and therefore
%
\begin{align}
%
    Q = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
            {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
%
\end{align}

On the other hand, from the first equation relating $Q$ and $\sigma^2$, we see that:
%
\begin{align}
%
    Q = \frac{A}{B - \sigma^2}.
%
\end{align}
%

Putting these together, we have:
%
\begin{align}
%
    \frac{A}{B - \sigma^2}
    = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
        {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
    = \frac{C - E \cdot \sigma^2}{D - F \cdot \sigma^2},
%
\end{align}
%
where
%
\begin{align}
%
    E = Q \cdot \1^\top x,
%
\end{align}
%
and
%
\begin{align}
%
    F = (2L+1) \cdot Q \cdot \1^\top x.
%
\end{align}

This is a quadratic equation for $\sigma^2$. Unfortunately, it can have two positive solutions, so I'm not sure if it helps...
\end{document}

>>>>

It will be notationally simpler to instead estimate $\beta \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$. From the first moment we estimate $\beta \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (\beta \cdot (\1^\top x))^2 
    &= \beta^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

On the other hand, from the second moment we can estimate $\beta \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $\beta\cdot T_2(0) + \sigma^2$, and consequently $B \equiv \beta \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$. Taking the ratio, we obtain the equation:
%
\begin{align}
%
    \frac{1}{\beta} + \frac{\sigma^2}{A} = \frac{B}{A}.
%
\end{align}

If we knew $\sigma$, we can solve for $\beta$:
%
\begin{align}
%
    \beta = \frac{A}{B - \sigma^2}.
%
\end{align}

@@

\section{A pair of quadratics satisfied by $\beta$}

It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments. The previous section gives the equation:
%
\begin{align}
%
    \beta = \frac{A}{B - \sigma^2}.
%
\end{align}
%

Now we move up to third-order moments. From the first order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (\beta \cdot \1^\top x) \cdot (\beta \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= \beta^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (\beta \cdot \1^\top x)
        \nonumber \\
    &= \beta^2 \cdot \omega + \sigma^2 \cdot E,
%
\end{align}
%
where 
%
\begin{math}
%
    \omega = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta),
%
\end{math}
%
and
%
\begin{align}
%
    E = \beta \cdot \1^\top x.
%
\end{align}

From the observed third-order terms themselves, we can estimate:
%
\begin{align}
%
    D \equiv \beta\cdot \omega + (2L+1)\cdot\sigma^2\cdot (\beta \cdot \1^\top x)
    = \beta\cdot \omega + \sigma^2\cdot F,
%
\end{align}
%
where
%
\begin{align}
%
    F = (2L+1)\cdot(\beta \cdot \1^\top x).
%
\end{align}

Consequently:
%
\begin{align}
%
    D\cdot \beta - \sigma^2 \cdot \beta  \cdot F
    = \beta^2 \cdot w = C - \sigma^2 \cdot E.
%
\end{align}
%
Using $\sigma^2 = B - A/\beta$ and rearranging, we get:
%
\begin{align}
%
    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE = 0.
%
\end{align}

\section{Relation to other work on blind deconvolution}

Blind deconvolution is a fundamental and well-studied problem in signal processing. Generally, models of the following form are considered:
%
\begin{align}
%
    Y = h \ast X  + \sigma N,
%
\end{align}
%
where $h$ is a fixed, non-random filter vector of length $L$, say; and $X$ is a length $n$ random vector; and $N$ is a random noise vector. Often, $X$'s entries are assumed to be iid.

Many previous works are focused on recovering the vector $X$ from the observed vector $Y$. A standard method in the $\sigma = 0$ regime involves solving for the unknowns $h$ and $Y$ by maximizing a third or fourth order cumulant of $Y$ \cite{cadzow1996blind}.

\bibliographystyle{plain}
\bibliography{refs_bmra}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save1.tex
updates on section 2

It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments. The previous section gives the equation:
%
\begin{align}
%
    \beta = \frac{A}{B - \sigma^2}.
%
\end{align}
%

@@

>>>>

It turns out that $\beta$ satisfies two independent quadratic equations, defined in terms of the observed third-order moments. The coefficients of these quadratics depend only on the observed moments, not on $\sigma$; so we can estimate $\beta$ (and hence $\gamma$) consistently, even without knowing the noise level. We can then estimate $\sigma$, and from them, recover the moments of $x$, which in turn lets us solve for $x$.

\subsection{The first quadratic equation}

The previous section gives the equation:
%
\begin{align}
%
    \beta = \frac{A}{B - \sigma^2}.
%
\end{align}
%

@@

\subsection{The second quadratic equation}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test4_save2.tex
updates on section 2

\newcommand{\F}{\mathcal{F}}
\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}

@@

Now we move up to third-order moments. From the first order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (\beta \cdot \1^\top x) \cdot (\beta \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= \beta^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (\beta \cdot \1^\top x)
        \nonumber \\
    &= \beta^2 \cdot \omega + \sigma^2 \cdot E,
%
\end{align}
%
where 
%
\begin{math}
%
    \omega = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta),
%
\end{math}
%
and
%
\begin{align}
%
    E = \beta \cdot \1^\top x.
%
\end{align}

@@

Consequently:
%
\begin{align}
%
    D\cdot \beta - \sigma^2 \cdot \beta  \cdot F
    = \beta^2 \cdot w = C - \sigma^2 \cdot E.
%
\end{align}
%
Using $\sigma^2 = B - A/\beta$ and rearranging, we get:
%
\begin{align}
%
    \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE = 0.
%
\end{align}

@@

>>>>

\renewcommand{\AA}{\mathcal{A}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\FF}{\mathcal{F}}

\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}

@@

Now we move up to third-order moments. From the first-order moments, we can estimate $\beta \cdot \1^\top x$; and from the second-order moments we can estimate $\beta \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (\beta \cdot \1^\top x) \cdot (\beta \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= \beta^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (\beta \cdot \1^\top x)
        \nonumber \\
    &= \beta^2 \cdot \omega + \sigma^2 \cdot E,
%
\end{align}
%
where 
%
\begin{math}
%
    \omega = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta),
%
\end{math}
%
and
%
\begin{align}
%
    E = \beta \cdot \1^\top x.
%
\end{align}

@@

Consequently:
%
\begin{align}
%
    D\cdot \beta - \sigma^2 \cdot \beta  \cdot F
    = \beta^2 \cdot w = C - \sigma^2 \cdot E.
%
\end{align}
%
Using $\sigma^2 = B - A/\beta$ and rearranging, we get:
%
\begin{align}
%
    & \beta^2 \cdot (D - BF) + \beta \cdot (AF + BE - C) - AE 
        \nonumber \\
    & \equiv \AA \beta^2  + \BB \beta  + \CC = 0.
%
\end{align}

@@

It is a straightforward computation to show that:
%
\begin{align}
%
    \phi &\equiv \left( \sum_{i=1}^L x_i \right)^3 
        \nonumber \\
    &= T_3(0,0) + 3\sum_{\Delta=1}^L T_3(\Delta,\Delta)
        + 3 \sum_{\Delta=1}^L T_3(0,\Delta) 
        + 6 \sum_{1 \le \Delta_1 < \Delta_1 \le L-1} T_3(\Delta_1,\Delta_2).
%
\end{align}

The quantity $E = \beta \cdot \1^\top x$ is observed, and hence so is $E^3 = \beta^3 \cdot \phi$.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save1.tex
updates on section 2

\begin{comment}

Actually, what Tamir meant when he said first moment was the average of the windows' averages (a scalar), not the average window (a vector). But this also converges a.s.\ to $\gamma \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows. The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$. Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
%
\begin{align}
%
    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
    = \gamma \cdot \bar{x}.
%
\end{align}

\end{comment}

@@

It will be notationally simpler to instead estimate $\beta \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$. From the first moment we estimate $\beta \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (\beta \cdot (\1^\top x))^2 
    &= \beta^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

@@

@@

@@

Combining these two equations, we arrive at the quadratic:
%
\begin{align}
%
    (B-H/O) \cdot \beta^2 - A \cdot \beta + (G / O) 
    \equiv \DD \beta^2 + \EE \beta + \FF = 0.
%
\end{align}
\end{document}

>>>>

@@

It will be notationally simpler to instead estimate $\beta \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$. From the first moment we estimate $\beta \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (\beta \cdot \1^\top x)^2 
    &= \beta^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= \beta^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

@@

Of course, for finite $n$ and large $\sigma$ the formulas for $\beta$ and $\sigma$ will be noisy. Consequently, I suggest instead adding them as variables to the non-linear least squares problem; that is, solve for all of $x$, $\beta$ and $\nu \equiv \sigma^2$ by fitting their moments to the observed moments via least-squares.

@@

We can simplify the expressions a little bit. First, we observe that:
%
\begin{align}
%
    \CC = -AE = -(\beta \cdot \1^\top x)^3 = -E^3 \equiv -G.
%
\end{align}

Second, we can simplify $\BB$:
%
\begin{align}
%
    \BB = AF + BE - C = (2L+1) \cdot G + 2E \beta \sum_{\Delta=1}^{L-1} T_2(\Delta).
%
\end{align}

@@

Combining these two equations, we arrive at the quadratic:
%
\begin{align}
%
    (B-H/O) \cdot \beta^2 - A \cdot \beta + (G / O) 
    \equiv \DD \beta^2 + \EE \beta + \FF = 0.
%
\end{align}

\subsection{Independence of the quadratics}

We can show that for generic $x$, the two quadratics are independent; and in fact, for all sufficiently large $\beta$, they are independent for any $x$ (not just generic). By ``generic'' I mean on a set with complement of Lebesgue measure 0.

To see this, it's enough to show that the ratio of coefficients is not the same. We have:
%
\begin{align}
%
    \frac{\BB}{\CC} = -(2L + 1) - \frac{2\beta \sum_{\Delta \ge 1}T_2(\Delta)}{E^2}
%
\end{align}
%
and
%
\begin{align}
%
    \frac{\EE}{\FF} = - (6L - 3).
%
\end{align}

Suppose the quadratics are dependent. Then $\BB / \CC = \EE / \FF$, or
%
\begin{align}
%
    2L + 1 + \frac{2\beta \sum_{\Delta \ge 1}T_2(\Delta)}{E^2} = 6L  - 3
%
\end{align}
%
or equivalently
%
\begin{align}
%
    4(L-1)\beta^2(\1^\top x)^2 
    &=  4(L-1)E^2 
        \nonumber \\
    &= 2 \beta \sum_{\Delta\ge1}T_2(\Delta) 
        \nonumber \\
    &= \beta ( (\1^\top x)^2 - \|x\|^2 ) .
%
\end{align}

Rearranging we get:
%
\begin{align}
%
    (4(L-1)\beta - 1)(\1^\top x)^2 + \|x\|^2 = 0.
%
\end{align}
%
This describes a quadratic which has measure zero. But we can actually say something more. Since $(\1^\top x)^2 \le L \|x\|^2$, we must have:
%
\begin{align}
%
    1 - 4(L-1)\beta = \frac{\|x\|^2}{(\1^\top x)^2} \ge \frac{1}{L}
%
\end{align}
%
i.e.
%
\begin{align}
%
    (L-1)(1 - 4L\beta) = L -1 - 4(L-1)L \beta \ge 0
%
\end{align}
%
so that we need $\beta \le 1 / (4L)$. In other words, if $\beta \ge 1 / (4L)$, then the quadratics are independent.

\section{Relation to system identification}

This problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, the user observes a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

The method of moments has been proposed as a solution to the system identification problem.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save10.tex
updates on section 2

This problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, the user observes a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

The method of moments has been proposed as a solution to the system identification problem.

>>>>

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead. One proposed heuristic for computing the maximization is to use Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}. The EM method is based upon a certain ``forward-backward'' procedure used in hidden Markov models, described in \cite{rabiner1989tutorial}.

Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}. This paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework. Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using fourth-order cumulants is described in \cite{giannakis1989id}.

%%%The problem of system identification should be distinguished from the related problem of blind deconvolution. In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save2.tex
updates on section 2

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead. One proposed heuristic for computing the maximization is to use Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}. The EM method is based upon a certain ``forward-backward'' procedure used in hidden Markov models, described in \cite{rabiner1989tutorial}.

Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}. This paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework. Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using fourth-order cumulants is described in \cite{giannakis1989id}.

%%%The problem of system identification should be distinguished from the related problem of blind deconvolution. In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$.

>>>>

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector. Note that the entries of $W$ do not need to be iid

A number of methods have been proposed for the system identification problem under various additional constraints. Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK. This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.

An entirely different approach based on expectation-maximization is described in TKTK.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save3.tex
updates on section 2

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector. Note that the entries of $W$ do not need to be iid

A number of methods have been proposed for the system identification problem under various additional constraints. Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK. This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.

An entirely different approach based on expectation-maximization is described in TKTK.

>>>>

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.

Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK. This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.

The problem of system identification should be distinguished from blind deconvolution. In the latter problem, the goal is to identify input signal $W$, rather than the filter $x$. TKTK

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save4.tex
updates on section 2

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification.

>>>>

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification. The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators. Another method based on third-order cumulants was described in \cite{giannakis1989id}.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save5.tex
updates on section 2

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}.

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification. The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators. Another method based on third-order cumulants was described in \cite{giannakis1989id}.

Under an assumption of ``higher-order independence'' on the input vector $W$, a version of the method of moments was considered in TKTK. This method uses the estimated third-order cumulants of the observed vector $Y$, and solves a linear system TKTK.

>>>>

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead. One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}. The EM method is based upon a certain ``forward-backward'' procedure described in \cite{rabiner1989tutorial}.

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification. The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators. Another method based on third-order cumulants is described in \cite{giannakis1989id}.

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save8.tex
updates on section 2

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead. One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}. The EM method is based upon a certain ``forward-backward'' procedure described in \cite{rabiner1989tutorial}.

Methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification. The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators. Another method based on third-order cumulants is described in \cite{giannakis1989id}.

>>>>

Likelihood-based methods seek to maximize the likelihood function for $x$, given the observed signal $Y$. Solving this optimization exactly is typically not tractable, and so heuristic methods are used instead. One proposed heuristic for computing the maximization is to Markov Chain Monte Carlo; in special cases, including the case where $W$ is binary, expectation-maximization has been used \cite{cappe1999simulation}. The EM method is based upon a certain ``forward-backward'' procedure used in hidden Markov models, described in \cite{rabiner1989tutorial}.

Because the likelihood approach is computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been used previously for system identification. The question of identifiablity of $x$ from moments for non-Gaussian $W$ was considered in \cite{lii1982deconvolution}; it was shown that under certain conditions on $W$, third-order statistics yield asymptotically consistent estimators. Another method based on third-order cumulants is described in \cite{giannakis1989id}.
